\section{Business case}

\subsection{Scientific aspects}

Improved tools for scientific research are constantly in the academic world to increase the rate and accuracy of research. By constructing a tool to aid researchers using MS data, they will be able to publish papers at an accelerated rate. The tool uses label-free MS data, which in turn is very useful for a number of reasons, one of which if you are doing clinical studies on large cohorts. Label-free MS data requires less preparation of samples than other methods, which utilizes labels. This mean finding biomarkers from biological samples could be improved, if you were to use the tool.

\subsection{Societal aspects}

As mentioned in the section above, the pipeline could speed up the studies meaning more practical usage of studies could be applied in a number of areas in society. As an example, if biomarkers were to be more easily discovered with the tool, this would mean more options for diagnosing patients would be available to hospitals, resulting in more accurate and earlier diagnoses of diseases in the population.

\subsection{Financial aspects}

The project is built from open-source programs, which will make it difficult to make the project commercially viable. The main dependencies are licensed under Apache License Version 2.0, which states that you are allowed to use the software for commercial purposes. This means that the software could technically be used in a commercial package.

However, if we were to widen the perspective and look at other areas which would benefit financially by the tool, any area using the tool could save money due to time savings using the pipeline and analysis of results. There would be less time developing customized pipelines and time analyzing the data due to everything is packaged in the container, meaning valuable time is saved for the same type of analysis, which in turn means less money used.
