\section{Stakeholder analysis}

A stakeholder analysis is a way to visualize which people will benefit from the project and their interests in the completion of the project.

\newcommand{\textone}{Lukas Käll is the supervisor of the project. His interest in the project is the highest, due to him being the creator of the program "Quandenser" alongside Matthew The. Creating an easy to use pipeline will make more researcher willing to switch over from their old tools to the new one which he has created}
\newcommand{\texttwo}{Peter Savolainen is the examiner of the project. His interest is to oversee the project as a whole to ensure that the project is finished in time}
\newcommand{\textthree}{Michael Jahn holds the data for the microbial data sets. His interests are that improved tools for analysis might yield more accurate results, thus making his research more precise}
\newcommand{\textfour}{SciLifeLaboratory is where the project is taking place. Researchers in SciLife might have some use for the end product of the project}
\newcommand{\textfive}{KTH is the main institution, which is interested in giving students their degree when they are finished}
\newcommand{\textsix}{A small area of science would benefit from the project, if I manage to create an easy to use pipeline which show superior performance for label-free quantification. Thus, their research could be improved by more accurate quantification tools}
\newcommand{\textseven}{Socieity does not have a large influence on the project, but improvements from the research with the pipeline might have a positive impact in the long run.}

\begin{table}[H]
\large
\resizebox{\textwidth}{!}{
\begin{tabular}{|p{4cm}|p{9cm}|}
\hline
Primary stakeholder & Description\\ \hline
Lukas Käll & \textone \\
Peter Savolainen & \texttwo \\
Michael Jahn & \textthree \\
ScilifeLaboratory & \textfour \\
KTH & \textfive \\
 & \\
 & \\ \hline
Secondary stakeholder & Description \\ \hline
Researchers & \textsix \\
Society & \textseven \\ \hline
\end{tabular}}
\caption{Stakeholder analysis}
\end{table}
