\section{Future work}

The pipeline has gotten some recognition over the course of it's creating and has been tested by researchers at SciLifeLab, Germany and Australia at the moment of writing. There are several improvements and future work that would be beneficial for the project.

\subsection{Further improvments of Quandenser parallelization}
The parallelization of the modified Quandenser could be improved in several fronts. The overhead calculations of for the modified Quandenser with the parallel option slows down the processing time, which increases the total amount of core hours required to complete the process, even if the wall time of the process is lowered. Some efforts has already been made to improve the overhead calculations by saving and loading parameters to simple text files, but the method of loading and saving data is rather slow and results in stability issues, due to missing data when saving only the essential parameters. However, the results only gives an insignificant speed boost for the processing.

As explained in the method section \ref{ssec:quandenser-method}, the parallelization of the minimum spanning tree cannot be "fully" parallelized (i.e. run all the calculations at the same time) and is unstable for large cohorts, due to the efforts mentioned above. Possible improvements in the modified version of Quandenser to rearrange the order of calculations in the minimum spanning tree to maximize the amount of possible parallel computations, would improve the calculation times for larger cohorts of samples, while also reducing the overhead processing time, due to a lesser depth of tree.

In summary, by further improving how the modified Quandenser loads and saves data from previous runs and rearranging the minimum depth tree would yield significant improvements of parallel computation times and stability of the parallel Quandenser option of the pipeline.

\subsection{Analyzing boxcar spectra}
A novel method of mass spectrometry data acquisition developed by researches at Matthias Mann Lab in Munich, which increases the resolution of MS1 spectra by making one lower resolution MS1 scan and then multiple, smaller high resolution MS1 scans in chunks, thus increasing the overall MS1 resolution of scans \cite{boxcar}. A custom python script was created and integrated into the latest version of Quandenser-pipeline (v0.071) to be able to utilize the new type of data from the data acquisition. The script merges MS1 and Boxcar in mzML files for processing in Quandenser, then restructures and outputs a new mzML file with combined MS1 spectra, with an increased resolution compared to regular MS1 scans. By enabling the option in the pipeline, all mzML files (including any non-mzML mass spectrometry files after conversion) will be analyzed for Boxcar spectra and merged if found.

A data set with boxcar data could possibly be analyzed to test for how well the increased resolution of MS1 spectra would yield for results. One such data set exists with patients before and after gastric bypass surgery, fully with data acquired with Boxcar scans, which would be interesting to analyze in the future \cite{boxcar-data}.
